Influence of galaxy rotation and outflows in the Lyman Alpha spectral line

### 2017-03-02 paper/paper.tex
only changes in results left

** Rotational effects should be clearly detected and characterized by MUSE.\\

** The V=0 emission is not necessary because of radiation escaping without scattering, but that the viewing angle can control that. \\

** This new LAE model is roughly consistent with observations.\\

TERMINAR...\\

@@

@@

	\item Rotations induces a Doppler shift of the only-outflow spectra.\\

	\item TERMINAR...\\
\end{itemize}

@@

** Differential rotation instead of solid body. \\
** Fit and observation's parameters with MCMC. \\

TERMINAR...\\

@@

\section*{Acknowledgments}

** Cluster Uniandes?

TERMINAR...\\

>>>>

Among the observational implications that this paper has over observations we select three principal ones. First, the rotational effects of the galaxy should be clearly detected and characterized by MUSE's high resolution data. The Doppler redshift is already visible in other observations, such as the one seen in Fig. 7 of Prescott et al. \cite{Prescott14}.\\

Second, the central ($V=0$) emission of the spectra seen in the results is a consequence of the viewing angle of the galaxy and can be controlled by it. This means that the reason is not necessary that radiation is escaping without scattering, as several authors have suggested (CITAS...).\\

Finally, all the spectra produced from this new LAE model is roughly consistent with observations. The consideration of adding the new rotation parameter to the standard only-outflow model found in literature is reasonable and very powerful. \vrot and its consequent viewing angle $\theta$ can modify the morphology of the \lya line in new different ways by keeping the model simplified.\\

@@

	\item Rotations induces a Doppler shift in frequency of the only-outflow spectra.\\

@@

\end{itemize}

@@

For future work regarding the model, we would like to implement a differential rotation for the LAE instead of solid body. Regarding result analysis, we would like to compare against observations in two ways. Firstly by using the kinematic observation obtained from newly observed LAEs. We could do a consistency check between their real spectra and the simulated one that our model would produce with the respective parameters. Secondly we would like to take a specific observed spectrum and fit it using MCMC in order to predict ranges for its parameters. \\

\subsection{Reproducibility}

@@

\section*{Acknowledgments}
The authors would like to acknowledge the high performance computational cluster (HPC) hosted by Universidad de los Andes, where we ran the simulations for CLARA. \\

We would also like to acknowledge the participants of the meeting \textit{Escape of Lyman radiation from galactic labyrinths} at Crete, Greece, for their valuable comments on this work, specially to Max Gronke and Christian Herenz. \\
